SunPy - Python for Solar Physics

### 2014-01-24 Sunpy_paper_0.4.tex
Fixed reference symbol and added url to packages in main file
First draft for Dev and Future as well lc tweaks.
Changed to minted typesetting for code examples in lc section.
Fix merge related issues
added my affil to title page
more changes
Added dps affiliation and name
Added bg for listing in main and map files, plus few typos fixed.  Also reorderd some sentence into s/c launch
added my author details to tex file

%Uncomment next line if AMS fonts required
%\usepackage{iopams}

\begin{document}

@@

\author{S J Mumford}
\address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of 
Mathematics and Statistics, The University of Sheffield, Hicks Building, 
Hounsfield Road, Sheffield, S3 7RH U.K.}

\author{J Bloggs}
\address{Wibble wiblle wiblle}

\ead{sunpy@googlegroups.com}

@@

\input{1-Introduction}

\input{2-Data_Types}

\input{3-Retrieval}

\input{4-Util}

\input{5-Dev}

\input{6-Future}

%%% References
\bibliography{sunpy_paper_0.4}{}

>>>>

\usepackage{natbib}
\usepackage{minted}
\definecolor{bg}{rgb}{0.95, 0.95, 0.95}
\usepackage{hyperref}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}
\usepackage{graphicx}
\graphicspath{{./images/}}
\newcommand*{\newblock}{Bibliography}
\begin{document}

@@

\author{The SunPy Community}
\address{\url{http://sunpy.org}}
\ead{sunpy@googlegroups.com}

\author{Stuart J Mumford}
\address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of 
Mathematics and Statistics, The University of Sheffield, Hicks Building, 
Hounsfield Road, Sheffield, S3 7RH U.K.}

\author{Steven Christe}
\address{NASA Goddard Space Flight Center, Greenbelt, U.S.A.}

\author{David P\'erez-Su\'arez}
\address{South African National Space Agency - Space Science,
Hospital Street, 7200 Hermanus, Western Cape, South Africa}

\author{Andrew R Inglis}
\address{NASA Goddard Space Flight Center, Greenbelt, USA}
\address{The Catholic University of America, Washington, DC, USA}

@@

\input{1-Introduction}
\label{sec:Intro}

\input{2-Data_Types}
\label{sec:DataTypes}

\input{3-Retrieval}
\label{sec:retrevial}

\input{4-Util}
\label{sec:util}

\input{5-Dev}
\label{sec:dev}

\input{6-Future}
\label{sec:future}

\section{Conclusion}

%%% References
\bibliographystyle{stunat}
\bibliography{Sunpy_paper_0.4}{}
